Emulsions Stabilized by Magnetic Ellipsoidal Particles: A Lattice Boltzmann Study

### 2025-04-01 chapters/paper1_new.tex

% In LB simulations of spinodal decomposition, a characteristic length
% scale can be obtained from the structure factor, defined in Section \ref{section:domain_size}. \cite{kendon_3d_1999,kendon_inertial_2001} 
% It is worth noting that this definition of average domain size does not necessarily yield values that coincide with the typical
% domain size observed visually in snapshots such as those shown in Figure~\ref{fig:microstructure_viz}. However, in a dynamic
% scaling regime, different measures of domain size are expected to differ only by a constant ratio. We found that the commonly 
% used measure \(L_1(t)\) tends to overestimate the observed domain size. Numerically, the calculation of the spherically 
% averaged structure factor is subject to poor statistics in the low \(k\)-shells, where the average \(|\vec{k}|\) of the 
% lattice sites differs from the nominal shell radius. Additionally, the measurement of \(L(t)\) in simulations with
% periodic boundary conditions is subject to finite size effects. More importantly, in suspensions of anisotropic particles, 
% We cannot expect that the structure factor is isotropic. Therefore, we also used the 3D structure factor to calculate a lateral domain 
% size in each Cartesian direction from the second moments also defined in Section \ref{section:domain_size}. 
% \cite{jansen_bijels_2011,gunther_timescales_2014} We add the additional processing calculating a parallel and perpendicular domain size
% from the results in each cartesian direction, defining $L_{\parallel}=L_z$ and $L_{\perp} = \frac{L_x+L_y}{2}$ we plot the structure factor of the structures in
% Figure \ref{fig:structure_factor}.

@@

@@

@@

>>>>

From figure \ref{fig:domain_size}, the jamming of the bijels were determined to occur after $\~50000$ timesteps, characterized as a plateauing
of the domain size. Qualitative differences in the domain size were observed in Figure \ref{fig:microstructure_viz} which originate from particles
reorienting to the direction of the applied field. To characterize the microstructure at the final timestep, we plot the domain size of the bijels
stabilized by ellipsoidal particles and compare them to what is obtained with spherical particles. We also compare the results obtained from the
first and second moment derived structure factors by plotting the directional domain sizes as a function of the applied field to characterize
domain anisotropy. An additional simplification is made where the domain size parallel to the magnetic field is defined as $L_{\parallel}=L_z$
and the average of the other domain sizes are defined as $L_{\perp} = \frac{L_x+L_y}{2}$.

@@

Figure \ref{fig:D2a_B} demonstrates that the first moment derived structure factor shows little change in the domain size as a function of the applied field for
all particle aspect ratios. The second moment derived domain sizes demonstrate that the application of magnetic fields create domain anisotropy in the microstructure
of bijels stabilized by ellipsoidal particles. Domain anisotropy is characterized as a divergence in the parallel and perpendicular domain sizes, seen in bijels
stabilized by ellipsoidal particles but not in bijels stabilized by spherical particles upon application of a magnetic field. The characteristics of this divergence
also differ for bijels stabilized by prolate particles and oblate particles. Bijels stabilized by prolate particles see an increase in $L_{\parallel}$ and a decrease in
$L_{\perp}$ upon application of a magnetic field, while bijels stabilized by prolate particles see the opposite. This response is also dependent on the applied field,
with the degree of response increasing from $\bar{B} = 0$ to $\bar{B} = 0.5$ before plateauing with field strengths applied above $\bar{B} = 0.5$.
The particle aspect ratio dependent response arises from the differences in the orientation of
the magnetic moment in prolate and oblate ellipsoids. In our simulations, the symmetry axis of prolate and oblate particles lies parallel to the long axis 
and short axis of the particle respectively. In addition to the geometrical constraints imparted by the shape of the particles, this results in the orientation of the
particles to differ upon application of the magnetic field.

@@

In Figure \ref{fig:D2a_B}, we quantitifed how the application of constant magnetic fields affects the microstructure of bijels stabilized by ellipsoidal particles
and demonstrated that microstrucutre anisotropy is generated as a function of the applied field and the particle aspect ratio. Another parameter that controls the
performance of porous materials is the tortuosity, characterized as the ratio between the parameter of interest in that system and the parameter of interest in
the bulk system. While multiple definitions exist such as the geometric, hydraulic and diffusive tortuosity exist, we use the diffusive tortuosity due to its
importance in characterizing porous material performance. A lower diffusive tortuosity in battery materials have been found to improve ion transport, reducing the
likelihood of Lithium dendrite formation and improving the charging speed and number of cycles before battery degradation. 
\cite{chen_tortuosity_2020, ebner_tortuosity_2014}. We calculate the using the method described in Section \ref{section:tortuosity}

@@

From Figure \ref{fig:tau_B}, the tortuosities calculated for bijels stabilized by spherical particles
